Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-05-24 snapshot_system/abs.tex
Append store chapter
chnge

\begin{abstract}
This paper proposes a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
In this work, we describe our working snapshot system implementation, and provide
early performance measurements for both deduplication impact and
snapshot operations.
Thank you!
\end{abstract}

>>>>

\begin{abstract}
A cloud environment that  hosts a large number of  virtual machines has
a high storage demand for frequent backup of system image snapshots.
Deduplication of data blocks can lead a big reduction of redundant blocks when
their signatures are identical. However it is expensive and less fault-resilient to perform a global comparison
of all data block signatures and let a data block share by many virtual machines. 
This paper studies a cluster-based design which collocates a lightweight
backup service with the cloud service and integrates multiple duplicate detection strategies that  
localize the deduplication as much as possible within each virtual machine.
The optimized design only requires a small amount of memory resource to conduct duplicate detection
and an analysis illustrates this design with deduplication localization  provides  better fault tolerance.
This  paper  provides an evaluation that shows this  proposed scheme can accomplish a high deduplication 
efficiency while sustaining a good backup throughput.

%This paper studies the      a VM snapshot storage architecture which adopts multiple-level selective deduplication to bring the benefits of fine-grained data reduction into cloud backup storage systems.
%In this work, we describe our working snapshot system implementation, and provide
%early performance measurements for both deduplication impact and
%snapshot operations.
\end{abstract}

### 2013-05-24 snapshot_system/intro.tex
chnge

\section{Introduction}
In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each instance of a guest operating system runs on a virtual machine, accessing
virtual hard disks represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
Because these image files are stored as regular files from the external point of view,
backing up VM's data is mainly done by taking snapshots of virtual disk images.

A snapshot preserves the data of a VM's file system at a specific point in time. 
VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}.

Frequent  backup of VM snapshots increases  the reliability of VM's hosted in a cloud.
For example, Aliyun, the largest cloud service provider by Alibaba in China, 
provides automatic frequent backup of VM images to strengthen the reliability of its service for all users.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
Using a backup service with full deduplication support~\cite{venti02,bottleneck08}
can identify content duplicates among snapshots to remove redundant storage content,  but the weakness is that it
either adds the  extra cost significantly or competes computing resource with the existing cloud services.
In addition, data dependence created by duplicate relationship among snapshots
adds the complexity in fault tolerance management, especially when  VMs can migrate around in the cloud.

Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
virtual disk image backup. Although we treat each virtual disk  as a file logically, its size is very large.
On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud every day. 
One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
resources so that most of resources is kept for regular cloud system services or applications.
Thus our objective is to exploit the characteristics of VM snapshot data and
pursue a cost-effective deduplication solution. 
Another goal  is to decentralize VM snapshot backup and  localize  deduplication as much as possible,
which brings the benefits for increased parallelism  and fault isolation.

%,extreme_binning09,sparseindex09
By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL.
As the result, different VMs tend to backup large amount of highly similar data.

@@

The following table shows the strength and weakness of some well-know deduplication systems:
\begin{table}
    \begin{tabular}{|l|l|l|l|}
        \hline
        ~           & Scalability & Low-cost & Full Dedup \\ \hline
        DDFS        & N           & N        & Y          \\ 
        Ex-bin      & Y           & Y        & N          \\ 
        Guo         & Y           & N        & N          \\ 
        iDedup      & N           & Y        & N          \\ 
        Founadation & N           & N        & Y          \\
        \hline
    \end{tabular}
\end{table}

>>>>

\section{Introduction}
In a cluster-based cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} 
and Alibaba Aliyun\cite{Aliyun},
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
%Backup  of virtual disks is relatively straightforward since
%these image files are stored as regular files from the external point of view,
%backing up VM's data is mainly done by taking snapshots of virtual disk images.

%A snapshot preserves the data of a VM's file system at a specific point in time. 
%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
For example, the Aliyun cloud , which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.
The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand and  
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
can effectively identify content duplicates among snapshots and  remove 
redundant storage content,  but the solution can be expensive and there is a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

This paper seeks for a low-cost architecture option and considers that
a backup service collocates  on  the cloud cluster with a minimum resource usage. 
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
On the other hand, comparing fingerprints  adds significant  memory cost. 
Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
Cloud providers often wish that the backup service only consumes  small or modest resources
with a minimal impact to the existing cloud services.  A 
recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
Another issue is that after deduplication, the most of data blocks are shared by many virtual machines.
Failure of such blocks would  have a catastrophic effect and many snapshots of virtual machines would be affected.
Furthermore, 
%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots compete for computing resource as well and that  needs
to be considered. That is  because data dependence created
by duplicate relationship among snapshots  adds processing complexity.
% especially when  VMs can migrate around in the cloud.

The paper proposes an integrated approach which uses  multiple duplicate detection strategies
integrating  version  detection, small-scope inner VM duplicate comparison
and controlled cross-VM comparison. 
The key idea of this approach is to localize duplicate detection within each virtual machine as much as possible
and minimize memory usage while delivering a decent deduplication efficiency. 
That brings the benefits for parallelism  utilization and fault isolation.
Our deletion strategy uses a double Boomer filer strategy for periodic mark-and-sweeping of expired data blocks.
We have developed a prototype system that runs a cluster of Linux machines running Zen.
The backup storage uses a standard distributed file system  with data replication and
we allocate more  replicas for the commonly-shared  data blocks among VM snapshots to enhance fault tolerance.

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{review} reviews background and related work.
Section~\ref{sec:framework}  discusses the  design framework and system architecture.
Section~\ref{sec:model}  analyzes the benefit of our approach for fault isolation. 
Section~\ref{exper} is our experimental evaluation that compare with the other approach.
Section~\ref{conc}  concludes this paper.

%We are seeking Unlike the previous work dealing with general file-level backup and deduplication, our problem is focused on 
%virtual disk image backup. Although we treat each virtual disk  as a file logically, its size is very large.
%On the other hand, we need to support parallel backup of a large number of virtual disks in a cloud every day. 
%One key requirement we face at Alibaba Aliyun is that VM snapshot backup should only use a minimal amount of system
%resources so that most of resources is kept for regular cloud system services or applications.
%Thus our objective is to exploit the characteristics of VM snapshot data and
%pursue a cost-effective deduplication solution. 
%Another goal  is to decentralize VM snapshot backup and  localize  deduplication as much as possible,

%,extreme_binning09,sparseindex09
\comments{
By observations on the VM snapshot data from production cloud, we found snapshot data duplication 
can be easily classified into two categories: \emph{inner-VM} and \emph{cross-VM}. Inner-VM duplication
exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL.
As the result, different VMs tend to backup large amount of highly similar data.

@@

The following table shows the strength and weakness of some well-know deduplication systems:
\begin{table}
    \begin{tabular}{|l|l|l|l|}
        \hline
        ~           & Scalability & Low-cost & Full Dedup \\ \hline
        DDFS        & N           & N        & Y          \\ 
        Ex-bin      & Y           & Y        & N          \\ 
        Guo         & Y           & N        & N          \\ 
        iDedup      & N           & Y        & N          \\ 
        Founadation & N           & N        & Y          \\
        \hline
    \end{tabular}
\end{table}
}
